---
title: "R Notebook"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}
library(tidyverse)
library(DT)
library(plotly)               # This package does interactive graphs
library(rtweet)               # This package accesses Twitter data
library(lubridate)  
```

```{r}
token <- create_token(
app ="",
consumer_key = "",
consumer_secret = "",
access_token = "",
access_secret = "")

get_token()        # this shows the token. make sure key is the same as consumer_key above
```

```{r}
realDonaldTrump <- get_timeline("Trump", n = 10000)
```


```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
realDonaldTrump %>% 
  select(hashtags) %>%                   # Focus on the hashtags
  unnest() %>%                           # Separate multiple hashtags
  mutate(hashtags = tolower(hashtags)) %>%      # make all hashtags lowercase
  count(hashtags, sort=TRUE) %>%                # count how often they appear
  datatable()                                   # create an interactive table
```
This is a table that shows in decending order Trumps most popular hashtags.

```{r echo=TRUE}
realDonaldTrump %>% 
  group_by(day = date(created_at)) %>%    # extract the date, group by it
  summarize(tweets_per_day = n())         # count the number of tweets each day
```
This is a table showing the number of tweets by day from Donald Trump.

```{r echo=TRUE}
realDonaldTrump %>% 
  group_by(day = date(created_at)) %>%    # extract the date, group by it
  summarize(tweets_per_day = n())  %>%
  summarize(mean(tweets_per_day))# count the number of tweets each day
```
This is the mean number of tweets per day by Donald Trump.

```{r echo=TRUE}
realDonaldTrump %>%
  mutate(day = date(created_at)) %>% 
  plot_ly(x = ~day) %>%                                        
  add_histogram() %>% 
  layout(title = "Number of tweets from realDonaldTrump")
```
This is a graph showing the number of tweets per day from Doanald Trump using a (plotly) function in Rstudio.

```{r}
tz(realDonaldTrump$created_at)

```
```{r}
realDonaldTrump %>% 
  mutate(time = with_tz(created_at, "America/New_York")) %>% 
  mutate(time = hour(time)) %>% 
  count(time) %>% 
  datatable(options = (list(pageLength = 24)), rownames = F)
```
This table show the peak tweeting hours for Donald Trump.

```{r}
realDonaldTrump %>% 
  mutate(time = with_tz(created_at, "America/New_York")) %>%    # convert to Eastern time zone
  mutate(time = hour(time)) %>%                                 # extract the hour
  plot_ly(x = ~time) %>%                                        # create plotly graph
  add_histogram()    %>%
  layout(title = "When Does realDonaldTrump Tweet?", 
         xaxis = list(title = "Time of Day (0 = midnight)"),
         yaxis = list(title = "Number of Tweets"))# make histogram
```
This is a histogram showing the peak tweeting hours for Donald Trump.
```{r}
realDonaldTrump %>% 
  mutate(Day = wday(created_at,           # find the weekday that the tweet was created
                    label = T)) %>%       # use labels (Sun, Mon, etc) rather than numbers
  count(Day) %>%                          # count the number of tweets each day
  datatable(rownames = F)
```
This is a table that shows by weekdays, tweets from Donald Trump.

```{r}
realDonaldTrump %>% 
  mutate(Day = wday(created_at,           # find the weekday that the tweet was created
                    label = T)) %>%       # use labels (Sun, Mon, etc) rather than numbers
  plot_ly(x = ~Day) %>%
            add_histogram() %>%
  layout(title = "realDonaldTrump Tweet By Week?", 
         xaxis = list(title = "By Day"),
         yaxis = list(title = "Number of Tweets"))# make histogram
```
This is a histogram showing Donald Trumps tweets by the days of the week.


```{r}
realDonaldTrump %>% 
  mutate(day = wday(created_at, label = T)) %>% 
  mutate(hour = hour(with_tz(created_at, "America/New_York"))) %>% 
  plot_ly(x = ~day, y = ~hour) %>% 
  add_histogram2d(nbinsx = 7, nbinsy = 24) %>%
  layout(title = "When Does realDonaldTrump Tweet?", 
         xaxis = list(title = "Day of the week"),
         yaxis = list(title = "Time of day ( 0 = midnight"))
```
This is a heat map that acts as a 2D graph. It shows both by week and time of the day that Donald Trump tweets.











